### 2021-10-11 paper.Rmd
some results stuff

```{r setup, include = FALSE}
library("papaja")
library("anticlust")
library("knitr")
options(digits = 2)
knitr::opts_chunk$set(message=FALSE, warning = FALSE, echo = FALSE, dev = "cairo_pdf")

@@

# Load required packages
library(dplyr)
library(ggplot2)
library(tidyr)

@@

# approximation at N > 100
# mean(filter(rel, N > 100)$rel) * 100

@@

First, I investigated how well maximizing the k-plus criterion approximates the ordinary k-means criterion at the same time. Figure 2 illustrates the relative values of $\mathit{SSE}$ that were found when optimizing $\mathit{SSE_{kplus}}$ as compared to the direct optimization of $\mathit{SSE}$. Generally, optimizing $\mathit{SSE_{kplus}}$ yields an adequate approximation of $\mathit{SSE}$. However, the quality of this approximation depends on the group sizes of the partition problem: For larger $N$, k-plus anticlustering very closely follows k-means anticlustering's performance with regard to optimizing $\mathit{SSE}$. For $N > 100$, $\mathit{SSE}$ was approximated to more than 99.99% when conducting k-plus anticlustering as compared to k-means anticlustering. The minimum approximation for N = 24 and K = 4 was ...

>>>>

```{r setup, include = FALSE}
library("papaja")
library("anticlust")
library("knitr")
library("dplyr")
library("ggplot2")
library("tidyr")
options(digits = 2)
knitr::opts_chunk$set(message=FALSE, warning = FALSE, echo = FALSE, dev = "cairo_pdf")

@@

@@

# approximation at N > 100
approx_n100 <- mean(filter(rel, N > 100)$rel) 
approx_n24_k4 <- mean(filter(rel, N == 24, K == 4)$rel)

# cut decimals after n decimals
cut_decimals <- function(x, n) {
  x <- as.character(x)
  x1 <- strsplit(x, "\\.")[[1]][1]
  x2 <- strsplit(x, "\\.")[[1]][2]
  x2 <- strsplit(x2, "")[[1]]
  as.numeric(paste0(x1, ".", paste(x2[1:n], collapse = "")))
}

@@

First, I investigated how well maximizing the k-plus criterion approximates the ordinary k-means criterion at the same time. Figure 2 illustrates the relative values of $\mathit{SSE}$ that were found when optimizing $\mathit{SSE_{kplus}}$---as compared to the direct optimization of $\mathit{SSE}$. Generally, optimizing $\mathit{SSE_{kplus}}$ yielded an adequate approximation of $\mathit{SSE}$. In particular, for large group sizes, there is virtually no sacrifice in $\mathit{SSE}$ when  $\mathit{SSE_{kplus}}$ is optimized: For $N > 100$, $\mathit{SSE}$ was approximated to more than `r cut_decimals(approx_n100, 4) * 100`% when conducting k-plus anticlustering as compared to k-means anticlustering. In the simulation, the worst approximation was found when the group sizes were smallest: for $N = 24$ and $K = 4$ was approximated to $\mathit{SSE}$ `r approx_n24_k4 * 100`%. Thus, the quality of the approximation depended on the group size: smaller groups led to worse approximations, while in general there was very little in $\mathit{SSE}$, expecially for larger groups.

In a next step, I compared k-means anticlustering, k-plus anticlustering and anticluster editing in their ability to equalize means and standard deviations between groups.

```{r, fig.cap = "Awesome caption", fig.height = 6.5, fig.width = 5}

ldf %>% 
  group_by(method, Objective, N, K) %>% 
  summarise(Mean = mean(value)) %>% 
  filter(Objective %in% c("means", "sd"), method != "random") %>% 
  ggplot(aes(x = N, y = Mean, colour = method)) + 
  geom_line(aes(colour = method), size = .7) + 
  geom_point(aes(colour = method, shape = method)) +
  facet_grid(cols = vars(Objective), rows = vars(K), scales = "free") + 
  theme_apa() +
  theme(
    legend.position = "top",
    legend.title = element_text()
  ) + 
  guides(
    linetype = guide_legend(title = "Method"),
    shape = guide_legend(title = "Method")
  ) +
  theme(
    legend.position = "top",
    legend.title = element_text()
  ) +
  scale_colour_grey(name = "Method")
